Cartograms with Dynamic Features

### 2022-03-25 paper/section/data.tex
draft: review

Obtaining the heterogenous data can be challenging, especially when an EHR dataset is involved \cite{wang2021EHRa}. The data acquisition involves multiple steps. The first step is to obtain both geospatial boundaries and EHR data that match one another. The second step is to pre-process the EHR data to remove empty and erroneous values. The final step is to transform the data into a format that is suitable for visualization.

@@

\bobgraph{Clinical Commissioning Groups Shapefile}

Clinical Commissioning Groups (CCGs) are the primary administrative and geographic unit of the National Health Service (NHS) in the UK \cite{nhsNHS}. The number of CCGs changes over time due to the NHS re-organization. The most up-to-date shapefile is available from the Open Geography portalx \cite{opengeographyportalxOpen}. We decided to use the CCG shapefile from 2020 at the time of writing, because there is still no public EHR data published based on the latest CCG re-organization that took place in 2021.

\bobgraph{River Features}

We used OpenStreetMap \cite{openstreetmapRelation} as our data source to obtain shapefiles for River Thames, River Trent and River Great Ouse in England. These rivers were chosen as they are well-known rivers and pass through regions with dense population, and provide informative geographical and topological cues.

@@

After acquiring the shapefiles, we used QGIS \cite{qgisWelcome} to manually adjust projections and scales, and merge them into one shapefile. Finally, mapshaper \cite{blochMapshaper} is used to convert the merged shapefile into a TopoJSON \cite{TopoJSON} file. TopoJSON eliminates redundant coordinates in the data, this improves the rendering speed of our implementation.

>>>>

Obtaining the heterogenous data can be challenging, especially when an EHR dataset is involved \cite{wang2021EHRa}. The data acquisition involves multiple steps. The first step is to obtain both geospatial boundaries and EHR data that match one another. The second step is to pre-process the EHR data to remove empty and erroneous values. The final step is to transform the data into a format that is suitable for cartograms.

@@

\bobgraph{Clinical Commissioning Groups Shapefile:} Clinical Commissioning Groups (CCGs) are the primary administrative and geographic unit of the National Health Service (NHS) in the UK \cite{nhsNHS}. The number of CCGs changes over time due to the NHS re-organization. The most up-to-date shapefile is available from the Open Geography portalx \cite{opengeographyportalxOpen}. We decided to use the CCG shapefile from 2020 at the time of writing, because there is still no public EHR data published based on the latest CCG re-organization that took place in 2021.

\bobgraph{River Features:} We used OpenStreetMap \cite{openstreetmapRelation} as our data source to obtain shapefiles for River Thames, River Trent and River Great Ouse in England. These rivers were chosen as they are well-known rivers and pass through regions with dense population, and provide informative geographical and topological cues.

@@

After acquiring the shapefiles, we used QGIS \cite{qgisWelcome} to manually adjust projections, translations and scales, and merge them into one shapefile. Finally, mapshaper \cite{blochMapshaper} is used to convert the merged shapefile into a TopoJSON \cite{TopoJSON} file. TopoJSON eliminates redundant coordinates in the data, this improves the rendering speed of our implementation.

### 2022-03-25 paper/section/introduction.tex
draft: review

Among the four types of cartograms categorized by \citea{nusrat2016State} (contiguous, non-contiguous, rectangular, and Dorling), a trade-off between types of accuracy is made (See \tableref{table:accuracy}). For this project we focus on non-contiguous cartograms like Demers cartograms, because they facilitate statistical comparison between regions and they can make good use of screen space. Building on Demers cartograms \cite{ian2002Cartogram}, we introduce and develop novel dynamic topological features, such as rivers, aiming to improve the readability and geographical accuracy without sacrificing statistical accuracy. We implement a new cartographic layout algorithm that includes these topological features into the layout of the nodes representing geographical regions. To minimize geographical errors and make efficient use of screen space, the algorithm also updates the position of rivers to accommodate the node layout. One of the major challenges involves is how to develop a layout algorithm that handles different types of nodes. In other words, the layout algorithm is novel because it handles different types of nodes: rectangular representing regions and polylines representing rivers. We then apply the algorithm to a real world case-study using an Electronic Health Records (EHR) dataset to assess the accuracy of our algorithm. We also present a user study demonstrating its effectiveness.

@@

>>>>

Among the four types of cartograms categorized by \citea{nusrat2016State} (contiguous, non-contiguous, rectangular, and Dorling), a trade-off between types of accuracy is made (See \tableref{table:accuracy}). For this project we focus on non-contiguous cartograms like Demers cartograms, because they facilitate statistical comparison between regions and they can make good use of screen space. Building on Demers cartograms \cite{ian2002Cartogram}, we introduce and develop novel dynamic topological features, such as rivers, aiming to improve the readability and geographical accuracy without sacrificing statistical accuracy. We implement a new cartographic layout algorithm that includes these topological features into the layout of the nodes representing geographical regions. To minimize geographical errors and make efficient use of screen space, the algorithm also updates the position of rivers to accommodate the node layout. We then apply the algorithm to a real world case-study using an Electronic Health Records (EHR) dataset to evaluate of our algorithm. We also present a user study demonstrating its effectiveness.

@@

\new{One of the major challenges involves is how to develop a layout algorithm that handles different shapes. In other words, the layout algorithm is novel because it handles different types of nodes: rectangular representing regions and polylines representing rivers. Another challenge we overcome in developing the algorithm is to revolve stalemate situations introduced by dynamic topological features while minimizing the geographical error.}

### 2022-03-25 paper/section/main.tex
draft: review

{
\begin{figure}[tb!]
    \centering
    \includegraphics[width=\columnwidth]{figure/flowchart.png}
    \caption{A flowchart showing our layout algorithm.}
    \label{fig:flowchart}
\end{figure}
}

\algoref{alg:UpdateNodePosition} and \figref{fig:flowchart} provide an overview of our algorithm. \textbf{Initialization:} We first load and render the CCG geospatial boundaries. For each CCG we compute the centroid and represent it using a small unit size square node with initial size, $ \nodeSize $. We start with small unit size squares because they do not overlap initially. \textbf{Node layout:} The basic algorithm is as follows: we first apply the Fast Node Overlap Removal (VPSC) algorithm \cite{dwyer2006fast} to remove overlaps. We chose VPSC over other node overlap removal algorithms because VPSC is able to provide spread minimization and node movement minimization while maintaining a good level of global shape preservation \cite{chen2020Node}. We gradually increase the node size by 1 unit at a time to ensure smooth transitions. An increase in size can cause the nodes to overlap. During overlap removal, we compute node trajectories (See \algoref{alg:check river intersection}) and translate nodes to their new position. Nodes that cross a river are translated back to their previous position. This procedure ends when 1) no node overlap is present; 2) no nodes cross a river. We then increase $ \nodeSize $ by one pixel and repeat the algorithm until the max node size $ \nodeSizeMax $ is reached. The gradual size increase process provides stability to the layout and helps minimize geographical error.

@@

\begin{algorithm}[tb!]
    \caption{Procedure to update node positions by removing overlap and prevent nodes from crossing rivers.}\label{alg:UpdateNodePosition}
    \textbf{Global variables:} \\
    $ \nodeList \gets $ a list of nodes representing CCGs \\
    $ \nodeSize \gets $ the current size of all nodes \\
    $ \nodeSizeMax \gets $ the maximum size of a node \\
    $ \stalemateMax \gets $ the maximum number of iterations indicating a stalemate \\

    \textbf{Local variables:} \\
    $ \nodeListVPSC \gets $ a list of nodes representing CCGs after VPSC \\
    $ \nodeListCross \gets True $ if any node in the list crosses a river \\
    $ \nodeCross \gets True $ if node crosses a river \\
    % $ \nodeListEach \gets $ a node in $ \nodeList $ \\
    $ \nodeListEachPrevious \gets $ the previous position of $ \nodeListEach $\\
    $ \nodeListVPSCEach \gets $ a node in $ \nodeListVPSC $, which is the position of $ \nodeListEach $ after VPSC \\

@@

                \State \Comment{We should merge two lists into one}
                \State $ \nodeListCross \gets False $
                \State $ \nodeListVPSC \gets $ RemoveOverlap ($ \nodeList $)

                \ForEach {$ \nodeListVPSCEach \in \nodeListVPSC $}

                    \If {$ \nodeListEach(x,y) \neq \nodeListVPSCEach(x,y) $}

                        \State $ \nodeCross \gets $ \Call{TestRiverIntersection}{$ \nodeListVPSCEachLine $}
                        \State $ \nodeListEach(x,y) \gets \nodeListVPSCEach(x,y) $

@@

                            \State $ \nodeListCross \gets True $
                            \State $ \nodeListEachStalemate \gets \nodeListEachStalemate + 1 $

                            \If{$ \nodeListEachStalemate < \stalemateMax $}

                                \State $ \nodeListEach(x,y) \gets \nodeListEachPrevious(x,y) $

@@

                                \State \Call{ProcessStalemate}{$ \nodeListEach, \nodeListVPSCEach $}
                                \State $ \nodeListEachStalemate \gets 0 $ \Comment{Reset counter}

@@

% \begin{algorithm}[tb!]
%     \caption{Procedure to update the position of a single node $ \node $.}\label{alg:move position}

%     \textbf{Input:} \\
%     $ \node \gets $ the node \\
%     $ \nodeVPSC \gets $ the node after running VPSC \\

%     \textbf{Output:} \\
%     Returns $ True $ if the node's position is updated. \\

%     \begin{algorithmic}[1]
%         \Procedure{TranslateNode}{$ \node, \nodeVPSC $}
%         \If{$ \node(x,y) = \nodeVPSC(x,y) $}
%             \item[] \Comment{Node position remains unchanged}
%             \State \Return{$ False $}
%         \EndIf

%         \State $ \node(x,y) \gets \nodeVPSC(x,y) $

%         \State \Return{$ True $}
%         \EndProcedure
%     \end{algorithmic}
% \end{algorithm}

@@

We use rivers as topological boundaries and prevent nodes from crossing them. The resolution of rivers can be adjusted by the user, as shown in \figref{fig:river resolution}, the number of edges is reduced from its original 10,170 to 65. We do not require a pixel-level river resolution as Demers cartograms do not represent geography at this level od detail, instead a resolution that matches the nodes is used. Enabling river simplification reduces the number of edge intersection tests that need to be performed. When a node's position changes, we test if the node's trajectory intersects any segment of a river. See \algoref{alg:check river intersection}. A bounding box intersection test between the edge defined by node translation and river edges can be performed to reduce the number of edge intersection detections required.

@@

    \textbf{Local variables:} \\
    $ \riverEdgeListEachLine \gets $ a river edge in $ \riverEdgeList $ \\ 
    $ \nodeBoundingBox, \riverEdgeBoundingBoxEach \gets $ the bounding boxes for $ \nodeLineNV $ and $ \riverEdgeListEachLine $ \\
    % $ \boundingBoxInt \gets $ boolean indicating $ \nodeBoundingBox $ intersects $ \riverEdgeBoundingBoxEach $ \\
    % $ \nodeEdge \gets $ the edge for $ \node $\\
    % $ \edgeBoxInt \gets $ boolean indicating $ \nodeEdge $ intersects $ \riverEdgeListEach $ \\

@@

        \ForEach{$ \riverEdgeListEachLine \in \riverEdgeList $}
            \State $ \nodeBoundingBox \gets $ GetBoundingBox ($ \nodeLineNV $)
            \State $ \riverEdgeBoundingBoxEach \gets $ GetBoundingBox ($ \riverEdgeListEachLine $)
            % \State $ \boundingBoxInt \gets $ TestIntersection ($ \nodeBoundingBox, \riverEdgeBoundingBoxEach $)
            % \If{$ \boundingBoxInt = True $}

            \If{$ \nodeBoundingBox ~intersect~ \riverEdgeBoundingBoxEach = True $}
                \State \Return{$ \nodeLineNV ~intersect~ \riverEdgeListEachLine $}
                \EndIf
        \EndFor

@@

As the VPSC always attempts to produce an optimal node layout where node distribution and translation are minimized, a node's translation path might be repeatedly intersecting a river due to congestion, creating a stalemate situation, as shown in \figref{fig:stalemate}. If a node is translated between two positions for $ \stalemateMax $ iterations, a corridor is constructed to break up the congestion. A corridor, $ c $, is a rectangle with a width of $ \CorridorWidth $ and a length of $ \CorridorLength $, formed by deriving two edges $ \EdgeParallelA $ and $ \EdgeParallelB $ such that $ \EdgeParallelA \parallel \EdgeParallelA \parallel \nodeLineNpP $ (See \figref{fig:corridor}C and D). All enclosed nodes are then translated by $ \nodeVectorNC $ to alleviate the congestion (See \figref{fig:corridor}D).

{
\begin{figure}[tb!]
    \centering
    \includegraphics[width=\columnwidth]{figure/stalemate.png}
    \caption{A stalemate situation is when a node's translation path $ \nodeVectorCN $ intersects a river for $ \stalemateMax $ times. A stalemate often occurs when the area is congested and the node is unable to move to a position that is not intersecting a river.}
    \label{fig:stalemate}
\end{figure}
}

{
\begin{figure}[tb!]
    \centering
    \includegraphics[width=\columnwidth]{figure/corridor.png}
    \caption{A stalemate occurs when a node's translation path $ \nodeVectorCN $ intersects a river for $ \stalemateMax $ times, as shown in A. To address the issue, we derive a corridor (orange rectangle in D) based on $ \node $ and $ \nodeVPSC $. All nodes within the corridor are translated based on $ \nodeVectorNC $, such that $ \nodeVectorNNn = \nodeVectorNinNinn $. In order to show a clear illustration, we place nodes sparsely in this figure.}
    \label{fig:corridor}
\end{figure}
}

@@

    \textbf{Local variables:} \\
    $ \Corridor \gets $ the corridor \\
    $ \nodePrevious \gets $ the previous position of $ \node $ (this here is confusing because $ \nodePrevious $ is actually $ \nodeVPSC $ in the previous iteration)\\
    $ \PointP \gets $ the point extending $ \nodeVectorNC $ such that $ \nodeLineWidthNtP = \CorridorLength $\\
    $ \EdgeParallelA, \EdgeParallelB \gets $ the edges parallel to $ \nodeLineNpP $ \\
    $ corridor \gets $ a rectangle formed by $ \EdgeParallelA $ and $ \EdgeParallelB $ \\

@@

            \State $ \PointP \gets $ \Call{DerivePoint}{$ \nodeVectorPC $, $ \CorridorLength $}

            \State $ \EdgeParallelA \gets $ \Call{DeriveParallelEdge}{$ \nodeVectorNpP $, $ \frac{\CorridorWidth}{2} $}

            \State $ \EdgeParallelB \gets $ \Call{DeriveParallelEdge}{$ \nodeVectorNpP $, $ -\frac{\CorridorWidth}{2} $}

@@

            \ForEach{$ \nodeInCorridorEach $ inside $ \Corridor $}

                \State $ \Vector{\nodeInCorridorEach ~\nodeInCorridorEachT} = \nodeVectorPC $

                \State $ \nodeInCorridorEach(x,y) \gets \nodeInCorridorEachT(x,y) $

>>>>

{
    \begin{figure}[tb!]
        \centering
        \includegraphics[width=\columnwidth]{figure/flowchart.png}
        \caption{A flowchart illustration of our layout algorithm. See also \algoref{alg:UpdateNodePosition} for more detail.}
        \label{fig:flowchart}
    \end{figure}

    \begin{figure}[tb!]
        \centering
        \includegraphics[width=\columnwidth]{figure/flowchart2.png}
        \caption{An awesome flowchart illustration of our layout algorithm. See also \algoref{alg:UpdateNodePosition} for more detail.}
        \label{fig:flowchart2}
    \end{figure}
}

\algoref{alg:UpdateNodePosition} and \figref{fig:flowchart} provide an overview of the process. \textbf{Initialization:} We first load and render the CCG geospatial boundaries. For each CCG we compute the centroid and represent it using a small unit size square node with initial size, $ \nodeSize $. We start with small unit size squares because they do not overlap initially. \textbf{Node layout:} The basic algorithm is as follows: we first apply the Fast Node Overlap Removal (FNOR) algorithm that solves the Variable Placement with Separation Constraints (VPSC) problem \cite{dwyer2006fast} in order to remove overlaps. We chose FNOR over other node overlap removal algorithms because FNOR is able to provide spread minimization and node movement minimization while maintaining a good level of global shape preservation \cite{chen2020Node}. We gradually increase the node size by 1 unit at a time to ensure smooth transitions. An increase in $ \nodeSize $ can cause the nodes to overlap. During overlap removal, we compute node trajectories (See \algoref{alg:check river intersection}) and translate nodes to their new position. Nodes that cross a river are translated back to their previous position. This procedure ends when 1) no node overlap is present; 2) no nodes cross a river. We then increase $ \nodeSize $ by one pixel and repeat the algorithm until the max node size $ \nodeSizeMax $ is reached. The gradual size increase process provides stability to the layout and helps minimize geographical error.

@@

\begin{algorithm}[tb!]
    \caption{Procedure to update node positions by removing overlap and prevent nodes from crossing rivers.}\label{alg:UpdateNodePosition}
    \textbf{Global variables:} \\
    $ \nodeList \gets $ a list of $ \node $ representing CCGs with the following properties: \\
    \-\hspace{1em} $ \nodeListCross \gets True $ if any $ \node $ in $ \nodeList $ crosses a river \\
    $ \nodeSize \gets $ the current size of all nodes \\
    $ \nodeSizeMax \gets $ the maximum size of a node \\
    $ \stalemateMax \gets $ the maximum number of iterations indicating a stalemate \\

    \textbf{Local variables:} \\
    $ \node \gets $ a node is an object with the following property: \\
    \-\hspace{1em} $ \node.x, \node.y, $ or $ \node(x,y) \gets $ the x and y coordinates of $ \node $ \\
    \-\hspace{1em} $ \nodeCross \gets True $ if $ \node $ crosses a river \\
    \-\hspace{1em} $ \nodePrevious \gets $ the previous position of $ \node $ \\
    \-\hspace{1em} $ \nodeFNOR \gets $ the translated position of $ \node $ \\

@@

                \State $ \nodeListCross \gets False $
                \State $ \nodeList \gets $ RemoveOverlap ($ \nodeList $)

                \ForEach {$ \node \in \nodeList $}

                    \If {$ \node(x,y) \neq \nodeFNOR(x,y) $}

                        \State $ \node(x,y) \gets \nodeFNOR(x,y) $
                        \State $ \nodeCross \gets $ \Call{TestRiverIntersection}{$ \nodeFNORLine $}

@@

                            \State $ \nodeListCross \gets True $
                            \State $ \nodeStalemate \gets \nodeStalemate + 1 $

                            \If{$ \nodeStalemate < \stalemateMax $}
                                \State \hskip-2em \Comment{Transalte back to previous position}
                                \State $ \node(x,y) \gets \nodePrevious(x,y) $

@@

                                \State \Call{ProcessStalemate}{$ \node, \nodeFNOR $}
                                \State $ \nodeStalemate \gets 0 $ \Comment{Reset counter}

@@

@@

We use rivers as topological boundaries and prevent nodes from crossing them. The resolution of rivers can be adjusted by the user, as shown in \figref{fig:river resolution}, the number of edges is reduced from its original 10,170 to 65. We do not require a pixel-level river resolution as Demers cartograms do not represent geography at this level od detail. Instead a resolution that matches the node size is used. Enabling river simplification reduces the number of edge intersection tests that need to be performed. When a node's position changes, we test if the node's trajectory intersects any segment of a river. See \algoref{alg:check river intersection}. A bounding box intersection test between the edge defined by node translation and river edges can be performed to reduce the number of edge intersection tests required.

@@

    \textbf{Local variables:} \\
    $ \riverEdgeLine \gets $ a river edge in $ \riverEdgeList $ \\ 
    $ \nodeBoundingBox, \riverEdgeBoundingBox \gets $ the bounding boxes for $ \nodeLineNV $ and $ \riverEdgeLine $ \\
    % $ \boundingBoxInt \gets $ boolean indicating $ \nodeBoundingBox $ intersects $ \riverEdgeBoundingBox $ \\
    % $ \nodeEdge \gets $ the edge for $ \node $\\
    % $ \edgeBoxInt \gets $ boolean indicating $ \nodeEdge $ intersects $ \riverEdgeListEach $ \\

@@

        \ForEach{$ \riverEdgeLine \in \riverEdgeList $}
            \State $ \nodeBoundingBox \gets $ GetBoundingBox ($ \nodeLineNV $)
            \State $ \riverEdgeBoundingBox \gets $ GetBoundingBox ($ \riverEdgeLine $)

            \If{$ \nodeBoundingBox ~intersect~ \riverEdgeBoundingBox = True $}
                \State \Return{$ \nodeLineNV ~intersect~ \riverEdgeLine $}
                \EndIf
        \EndFor

@@

As the FNOR always attempts to produce an optimal node layout where node distribution and translation are minimized, a node's translation path might repeatedly intersect a river due to congestion, creating a stalemate situation, as shown in \figref{fig:stalemate}. If a node is translated between two positions, $ \node $ and $ \nodeFNOR $, for $ \stalemateMax $ iterations, we introduce a heuristic solution: constructing a corridor to break up the congestion. A corridor, $ c $, is a rectangle with a width of $ \CorridorWidth $ and a length of $ \CorridorLength $, formed by deriving two edges $ \EdgeParallelA $ and $ \EdgeParallelB $ such that $ \EdgeParallelA \parallel \EdgeParallelA \parallel \nodeLineNtNc $ (See \figref{fig:corridor}C and D). All enclosed nodes are then translated by $ \nodeVectorTC $ to alleviate the congestion (See \figref{fig:corridor}D).

{
\begin{figure}[tb!]
    \centering
    \includegraphics[width=\columnwidth]{figure/stalemate.png}
    \caption{A stalemate situation is when a node's translation path $ \nodeVectorCT $ (in iteration 1) intersects a river for $ \stalemateMax $ times. The node is translated back to its previous position (iteration 2). A stalemate often occurs when the area is congested and the node is unable to translate to a position without intersecting a river.}
    \label{fig:stalemate}
\end{figure}
}

{
\begin{figure}[tb!]
    \centering
    \includegraphics[width=\columnwidth]{figure/corridor.png}
    \caption{A stalemate occurs when a node's translation path $ \nodeVectorCT $ intersects a river for $ \stalemateMax $ times, as shown in A. To address the issue, we derive a corridor (orange rectangle in E) based on $ \node $ and $ \nodeFNOR $. All nodes within the corridor are translated based on $ \nodeVectorTC $, such that $ \nodeVectorNNn = \nodeVectorNinNinn $. In order to show a clear illustration, we place nodes sparsely in this figure.}
    \label{fig:corridor}
\end{figure}
}

@@

    \textbf{Local variables:} \\
    $ \Corridor \gets $ the corridor \\
    $ \PointP \gets $ the point extending $ \nodeVectorTC $ such that $ \nodeLineWidthNtP = \CorridorLength $\\
    $ \EdgeParallelA, \EdgeParallelB \gets $ the edges parallel to $ \nodeLineNtNc $ \\
    $ corridor \gets $ a rectangle formed by $ \EdgeParallelA $ and $ \EdgeParallelB $ \\

@@

            \State $ \PointP \gets $ \Call{DerivePoint}{$ \nodeVectorTC $, $ \CorridorLength $}

            \State $ \EdgeParallelA \gets $ \Call{DeriveParallelEdge}{$ \nodeVectorNtP $, $ \frac{\CorridorWidth}{2} $}

            \State $ \EdgeParallelB \gets $ \Call{DeriveParallelEdge}{$ \nodeVectorNtP $, $ -\frac{\CorridorWidth}{2} $}

@@

            \ForEach{$ \nodeInCorridor $ inside $ \Corridor $}

                \State $ \Vector{\nodeInCorridor ~\nodeInCorridorT} = \nodeVectorTC $

                \State $ \nodeInCorridor(x,y) \gets \nodeInCorridorT(x,y) $

### 2022-03-25 paper/section/related.tex
draft: review

\subsection{Implementations}

@@

One of the disadvantages of Dorling and Demers cartograms is the legibility. The layout algorithms may displace regions far from their original position and making them more difficult to interpret. Our work extends Demers cartograms. We introduce a new type of dynamic topological feature, a river, aiming to improve the interpretation, readability, and geographical accuracy of this class of cartograms.

>>>>

\new{Our work extends the algorithm described by \citea{tong2018cartograms} which incorporates static topological features into Demers cartograms. Making topological features dynamic further improves the geographical accuracy and legibility.}

\subsection{Implementation in Popular Media}

@@

One of the disadvantages of Dorling and Demers cartograms is the legibility. The layout algorithms may displace regions far from their original position and making the maps more difficult to interpret. Our work extends Demers cartograms. We introduce a new type of dynamic topological feature, a river, aiming to improve the interpretation, readability, and geographical accuracy of this class of cartograms.
